\begin{thebibliography}{9}
	\bibitem{osborne} 
	Martin J. Osborne. A Course in Game Theory
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004.
	
	\bibitem{crowds} 
	David Easley and Jon Kleinberg. Crowds, Networks and Markets
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004.
	
	\bibitem{axelrod} 
	Robert Axelrod. The Evolution of Cooperation
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004.
	
	\bibitem{other} 
	Multidimensional graph one
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004. 
	
	\bibitem{epstein} 
	J. Epstein. "Modelling Civil Violence"
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004. 
	
	\bibitem{tyranny} 
	Timothy Snyder. "On Tyranny"
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004. 
	
	\bibitem{3.5} 
	Erica Chenoweth. "3.5 result pretty cool huh"
	\textit{Journal}. 
	76, no. 1 (2008): 201-15. doi:10.1016/j.anbehav.2008.02.004. Info on 'knowledgenuts.com' in an article called 'strange secret of a successful revolution
	
	\bibitem{noc} 
	Daniel Shiffman. "Nature of Code"
	\textit{Journal}. 
	76, no. 1 (2008): 201-15.
	
	\bibitem{eq_of_life} 
	Martin A. Nowak. "Evolutionary Dynamics: Exploring the Equations of Life"
	\textit{Book}. 
	
	\bibitem{barabasi-albert} 
	Albert Barabasi Networks
	
	\bibitem{meme-epidemic}
	"An epidemiological approach to model the viral propagation of memes" "Applied Mathematical Modelling",  Lin Wang and Brendan Wood
	
	\bibitem{selfish-gene}
	R. Dawkins
	The Selfish Gene
	Oxford University Press (1976)
	
	\bibitem{kermack-mckendrick}
	Kermack, W. O. and McKendrick, A. G. "A Contribution to the Mathematical Theory of Epidemics." Proc. Roy. Soc. Lond. A 115, 700-721, 1927. 
	
	\bibitem{models-epidemiology}
	Mathematical Models in Population Biology and Epidemiology. Chapter 9.
	
	\bibitem{martcheva}
	`An Introduction to Mathematical Biology' by M. Martcheva
	
	\bibitem{mass-action}
	Mass action kinetics
	
	\bibitem{exact-SIR}
	Harko T. et al. Exact Analytical Solutions to SIR model
	
	\bibitem{b-r-n}
	Basic reproductive numbers from WHO. Althaus, Christian L. (2014). "Estimating the Reproduction Number of Ebola Virus (EBOV) During the 2014 Outbreak in West Africa". PLoS Currents. 6. doi:10.1371/currents.outbreaks.91afb5e0f279e7f29e7056095255b288
	
	\bibitem{arab-spring-percent}
	Who Participated in the Arab
	Spring? A Comparison of 
	Egyptian and Tunisian Revolutions 
	
	\bibitem{abm-gilbert}
	Agent-Based Models, Nigel Gilbert
	
	\bibitem{kroese-uppal}
	Kroese, J. and Uppal, A. (2017). A critical review of ‘Self-organized aerial displays of thousands of starlings: a model’ Unpublished manuscript, McGill University.
	
	\bibitem{networks}
	Newman, M.E.J. (2010). Networks, Oxford University Press.
	
	\bibitem{simmel}
	Georg Simmel, Soziologie. (1908)
	
	\bibitem{strength-weak}
	Granovetter, M. The Strength of Weak Ties (1973), article.
	
	\bibitem{galla}
	Galla, T 2017, Advanced Statistical Physics, lecture notes, Advanced Statistical Physics PHYS40571, University of Manchester, delivered 18 September 2017.
	
	\bibitem{scale-free-rare}
	Broido, A. D. and Clauset A. Scale-free networks are rare.
	
	\bibitem{ba-cluster}
	Bollob\'as, B. Mathematical results on scale-free random graphs, 2003.
	
	\bibitem{watts-strogatz}
	Watts, D. J. and Strogatz, S. H. Collective dynamics of `small-world' networks, Science 296, 1302-1305 (2002)
	
	\bibitem{num-fb-users}
	eMarketer, and Squarespace. Number of Facebook users in the United States as of January 2018, by age group (in millions). https://www.statista.com/statistics/398136/us-facebook-user-age-groups/ (accessed February 28, 2018). 
	
	\bibitem{fb-ego-data}
	https://snap.stanford.edu/data/egonets-Facebook.html
	
	\bibitem{friendster-data-archive}
	https://archive.org/details/friendster-dataset-201107
	
	\bibitem{friendster-data-stanford}
	https://snap.stanford.edu/data/com-Friendster.html
	
	\bibitem{econophysics1} Dragulescu, A and Yakovenko, V. Statistical Mechanics of Money, Income, and Wealth: A Short Survey. November, 2002 https://arxiv.org/pdf/cond-mat/0211175v1.pdf
	
	\bibitem{dragulescu}
	Statistical mechanics of money
	Adrian Dragulescu, Victor M. Yakovenko
	https://arxiv.org/abs/cond-mat/0001432
	
	\bibitem{econophysics2} Milakovic, M. A Statistical Equilibrium Model of Wealth Distribution. February, 2001 https://editorialexpress.com/cgi-bin/conference/download.cgi?db\_name=SCE2001\&paper\_id=214
	
	\bibitem{boltzmann-tutorial} Tutorial on using Mesa http://mesa.readthedocs.io/en/latest/intro-tutorial.html
	
	\bibitem{bernoulli}
	D. Bernoulli
	Réflexions sur les avantages de l’inoculation
	Mercure de Paris (1760)
	p. 173
	
	\bibitem{threshold-models-social-influence}
	Threshold Models of Social Influence
	Christopher Winship
	The Oxford Handbook of Analytical Sociology
	Edited by Peter Bearman and Peter Hedström
	Print Publication Date:
	Jan 2011
	Subject:
	Sociology
	Online Publication Date:
	Jun 2017
	DOI:
	10.1093/oxfordhb/9780199215362.013.20
	
	\bibitem{granovetter}
	Granovetter, M. S. (1978), ‘Threshold Models of Collective Behavior’, American Journal of Sociology, 83: 1420–43.
	
	\bibitem{p-d-goods} https://balentine.com/the-prisoners-dilemma-in-oil/
	
	\bibitem{p-d-nature} https://www.scientificamerican.com/article/game-theory-calls-cooperation-into-question1/
	
	
	\bibitem{axelrod-github}
	@misc{Axelrod-Pythonprojectteam2015,
		author = {Axelrod-Python project team},
		title = {{Axelrod-Python vx.y.z}},
		url = {http://axelrod-python.github.io/},
		year = {2015}
	}

	\bibitem{graph-theory-reference}
	Reinhard Diestel Graph Theory (check this reference) for undirected graph reference
	
\end{thebibliography}